---
title: "CM2024"
author: "Roemer Ibelings"
date: '2024-02-14'
output:
    flexdashboard::flex_dashboard:
        storyboard: true
        theme: bootstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(spotifyr)
library(plotly)
library(compmus)
```

### Dendogram / Heatmap

```{r, echo = FALSE}
dendogram_plot <- readRDS(file = "data/dendogram-plot.RDS")
dendogram_plot
```

*** 

Here a dendogram is showed of the playlist "Salsa covers" containing all the covers of songs latin style in this corpus. You could argue there are 2 or 4 groups in this playlist. The method used is complete because this gave the best results.


### Classification
```{r, echo = FALSE}
workflow_plot <- readRDS(file = "data/workflow-plot.RDS")
workflow_plot

indie_features_plot <- readRDS(file = "data/indie_features-plot.RDS")
indie_features_plot
```

***

### Tempogram

```{r, echo = FALSE}
tempo_plot1 <- readRDS(file = "data/tempo-plot1.RDS")
tempo_plot1

tempo_plot2 <- readRDS(file = "data/tempo-plot2.RDS")
tempo_plot2
```

***

These are two tempograms of the song I will survive by Gloria Gaynor. The second one actually is the latin remake called Yo Vivire, which translates to I will survive. The original song is a bit faster than the latin song, what I did not expect. Both tempograms are Fourier-based. As you can see the latin remake one is a lot clearer than than the original. This is probably because of the percussion.

### Introduction {data-commentary-width=400}

*** 

I want to conduct research on the differences between music from Latin America and the West. To achieve this, I curated a corpus consisting of two playlists. The first list comprises of "Latin-remake" versions of well-known Western songs, while the second list consists of the original versions of these songs. My aim is to investigate what makes a song sound distinctly Latin. Are there underlying structures at play? Perhaps it's in the instrumentation; features like timbre.



### Histogram


### Chroma features


### Self similarity matrix

```{r, echo = FALSE}
ssm_plot1 <- readRDS(file = "data/ssm-plot1.RDS")
ssm_plot1

ssm_plot2 <- readRDS(file = "data/ssm-plot2.RDS")
ssm_plot2
```

***

In these self similarity matrices I compared the song Fur Elise with it the Latin remake version of it. I chose this one because it's one of the few songs in the corpus without singing on it. After fidgeting with the features of the self similarity matrix I found this similar pattern in both songs. The settings of both the matrices are set so you can see the similarity in timbre. After listening to both songs I found out that a certain high pitched piano piece must be this. Unfortunately I did not find any difference between both playlists, which could indicate what makes a latin song. But this similarity could maybe contribute later in the research.


### Key and Chord analysis

```{r, echo = FALSE}
keygram_plot1 <- readRDS(file = "data/keygram-plot1.RDS")
keygram_plot1

keygram_plot2 <- readRDS(file = "data/keygram-plot2.RDS")
keygram_plot2
```

*** 

Here two keygrams are presented. They both are of the song called "I love rock and roll". The first keygram is of the original by Joan Jett & The Black Hearts. The second is a latin remake by The Mariachis. 

I chose this song to show the dissimilarity in key between the original and latin remake. When listening to these two songs the original is with heavy guitars and the latin remake is well... very latin sounding; accoustic guitar and trumpets.

As you can see the original song is played in E major and E minor. The remake is played in A minor. The blue column after 150 seconds is due to a percussion heavy bridge in the song.


### Track level summaries

```{r, echo=FALSE}
jazz_plot1 <- readRDS(file = "data/jazz-plot1.RDS")
jazz_plot1

jazz_plot2 <- readRDS(file = "data/jazz-plot2.RDS")
jazz_plot2
```


### Novelty functions

```{r, echo = FALSE}
novelty_func_plot1 <- readRDS(file = "data/novelty_func-plot1.RDS")
novelty_func_plot1

novelty_func_plot2 <- readRDS(file = "data/novelty_func-plot2.RDS")
novelty_func_plot2

novelty_func_plot3 <- readRDS(file = "data/novelty_func-plot3.RDS")
novelty_func_plot3
```


### Conclusion


