---
title: "CM2024"
author: "Roemer Ibelings"
date: '2024-02-14'
output:
    flexdashboard::flex_dashboard:
        storyboard: true
        theme: bootstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(spotifyr)
library(plotly)
```

### Introduction {data-commentary-width=400}

```{r}
```

*** 

African music has found it's way to the Western hit lists nowadays. I want to research the difference between traditional african music and the African music from nowadays. Are still elements that can be found in both?

### Analysis 

```{r, echo = FALSE}
traditional <- get_playlist_audio_features("", "4sLTOwxhhj8yDJAxjPz0KZ")
hits2023 <- get_playlist_audio_features("", "4ZtmMuXoeI14XT7pubLq70")

traditional_plot <- ggplot(traditional, aes(danceability)) +
  geom_histogram(binwidth = 0.1, fill = "red") +
  ggtitle("Traditional") +
  geom_vline(aes(xintercept=mean(danceability)))

hits2023_plot <- ggplot(hits2023, aes(danceability)) +
  geom_histogram(binwidth = 0.1, fill = "blue") +
  ggtitle("Hits 2023") +
  geom_vline(aes(xintercept=mean(danceability)))

ggplotly(traditional_plot)
ggplotly(hits2023_plot)
```

***

These plots show the difference in danceability between the traditional and the hits from now. It also shows the mean. I ofcourse need to work more on it. I'm also aware of the fact that maybe African music is way too broad of a topic.

### Conclusion

```{r}
```



